\documentclass[12pt]{article}
\title{EE445M Lab 4}
\author{Hershal Bhave (hb6279) and Eric Crosson (esc625)}
\date{Friday April 03, 2015}

\usepackage[in]{fullpage}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{cleveref}
\usepackage[nosolutionfiles]{answers}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdfpages}
\usepackage{float}
\usepackage{subcaption}

\newenvironment{Ex}{\textbf{Problem}\vspace{.25em}\\}{}
\Newassociation{solution}{Soln}{Answers}
\pagebreak[3]
\newcommand{\Opentesthook}[2]{\Writetofile{#1}{\protect\section{#1: #2}}}
\renewcommand{\Solnlabel}[1]{\textbf{Solution}\quad}
\newcommand{\todo}{{\LARGE \emph{\color{red}TODO}}}
\newcommand{\ohm}{$\Omega$}
\newcommand{\hbr}{\hfill\vspace{.25em}\\}
\newcommand{\dd}[1]{\:\mathrm{d}{#1}}
\newcommand{\ddt}[1]{\frac{\dd{}}{\dd{#1}}}
\newcommand{\dddt}[1]{\frac{\dd{}^2}{\dd{#1}^2}}

\definecolor{mygreen}{rgb}{0,0.6,0}
% \definecolor{mygreen}{rgb}{0.13,0.55,0.13}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{
  backgroundcolor=\color{white},
  basicstyle=\scriptsize\ttfamily,
  breakatwhitespace=false,
  breaklines=true,
  captionpos=b,
  commentstyle=\color{mygreen},
  deletekeywords={...},
  escapeinside={\%*}{*)},
  extendedchars=true,
  frame=single,
  keywordstyle=\color{blue},
  rulecolor=\color{black},
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  stringstyle=\color{mymauve},
  tabsize=2,
  title=\lstname,
  columns=fullflexible,
}

\begin{document}
\maketitle

\section{Objectives}
\begin{itemize}

\item Interface a SD card to the TM4C123 SPI port.
\item Address translation from logical to physical address.
\item Write a file-system driver.
\item Implement a disk storage protocol.
\item Develop a simple directory system.
\item Stream debugging information onto the disk.
\item Add commands to your interpreter to test and evaluate the
  solid-state disk.
\end{itemize}

\section{Hardware Design}
None in this lab.

\section{Software Design}
Reference \cref{lst:ff-h,lst:ff-c,lst:shell-h,lst:shell-c}

\section{Measurement Data}
\begin{table}
  \centering
  \caption{SDCard Read/Write Bandwidth}
  \begin{tabular}{c|c}
    Read Bandwidth & Write Bandwidth \\
    \hline
    something & something \\
  \end{tabular}
  The SPI clock rate is 8 MHz, confirmed by oscilloscope and code. The
  bandwidth is 51 kbytes/sec.
  inspection.
\end{table}
\section{Analysis and Discussion}


\newpage
\section{Code}
%% \lstinputlisting[language=C,label=lst:ff-h,caption=\texttt{ff.h}]{@doc-staging-area@/ff.h}
%% \lstinputlisting[language=C,label=lst:ff-c,caption=\texttt{ff.c}]{@doc-staging-area@/ff.c}
%% \lstinputlisting[language=C,label=lst:shell-h,caption=\texttt{shell.h}]{@doc-staging-area@/shell.h}
%% \lstinputlisting[language=C,label=lst:shell-c,caption=\texttt{shell.c}]{@doc-staging-area@/shell.c}

\end{document}
